A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-08-12 01_Meta-analysis_experiments.Rmd
move text to first chapter

# Studies considered in meta-analysis

@@

We need to focus the meta-analysis on fungicides with the same mode of action.
Let's look at all the fungicides and retain the best represented fungicide group in the data.
```{r Fungicides}
PM_MB_dat %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise(groups = 'drop') %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
   scale_colour_usq() +
   coord_flip()
```

Tebuconazole and propiconazole are both classed as demethylase inhibitors. 
We will retain the trials trials which only contain DMI fungicides.  
```{r}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref, location, year)%>%
   arrange(year)
```
We will retain all fungicides for now and remove them before the analysis.

>>>>

# Trials considered for inclusion in meta-analysis

@@

We need to focus the meta-analysis on fungicides with the same mode of action.
Let's look at all the fungicides and retain the best represented fungicide group in the data.
```{r Fungicides}
PM_MB_dat %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise(groups = 'drop') %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
   scale_colour_usq() +
   coord_flip()
```
The demethylation inhibitors (DMI), tebuconazole and propiconazole, are used in the highest frequencies.
The DMIs have the same fungicide mode of action and are good candidates to be pooled in the meta-analysis.

Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.

Perhaps best way forward is to focus the meta-analysis on only the DMIs.
This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.

We will retain the trials trials which only contain DMI fungicides.  
```{r}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref, location, year)%>%
   arrange(year)
```
We will retain all fungicides for now and remove them before the analysis.
